Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-01 neurips-20/cvx-flats.tex
Sections 1 and 2 pass

\section{Introduction}\label{sec:intro}
\raf{General comment: see if you can make the intro less of an explanation to someone who has never heard of consistency, etc, and more of a ``reminder'' and recap of what's been going on in the field, culminating in the gap between what is out there and what we would like to know -- the gap that we fill}
\raf{General style: see if you can make the writing sharper, with less passive voice.  See if you can channel some Hemmingway and boil each sentence down to the key point.}
\jessie{Alright, I tried...}
In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or there is no target loss.
When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
In continuous estimation settings, one often starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value.
We are able to generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
%For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
\raft{I think few ML people know anything about pinball loss... I think we should de-emphasize the continuous setting in the intro, and include it in passing.}\jessie{Removed the sentence, but probably want to at least allude to it?}
The statistical guarantees we desire from a surrogate are \emph{consistency}: a precursor to excess risk bounds and rates.
%\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}
We are particularly interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting. 
We would also like our surrogate losses to be efficient in the dimension of the input, as this is one potential source of significant computational speedup.

%\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.  E.g. ``Our results give two contributions to this field.  First, .....  Second, .....''  Something like that before going into the theorems.}
Our results contribute two major findings to this field.
First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
This allows us to use property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
\raft{Cleaned up this prev sentence} \jessiet{Noted... much better how it is now.}
Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.

@@

\raf{I'm usually against these sorts of sections if they are truly just a roadmap.  See if you can make it flow less like a table of contents and more like a list of contributions with references to where in the paper to find them.  E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.} \raft{Exactly, well done}\jessiet{Phew; feel free to delete this thread now.}
%actually tell the reader
After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
\raft{Not a characterization!}\jessiet{right.... whoops.}
the existence of consistent convex surrogates in a given dimension $d$.
This result is closely related to those provided by~\cite[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
Moreover, in continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
Property elicitation is the main tool to understand consistency dimension in this case, and insights from our main result answer an open question posed by~\cite[Section 8]{frongillo2018elicitation}.

@@

We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} (or prediction space) $\R$, which may be different from $\Y$.
For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.

In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate prediction with $u \in \reals^d$.
A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and a surrogate $L$ is \emph{convex} if it is convex in the prediction space for every outcome $y \in \Y$.

@@

\bo{What about introducing the quadrants here? Something like: ``Instead of a target loss, in some estimation problems, one is given a target \emph{property}: [say what a property is]. The goal is to learn $f$ that approximately outputs the property on the conditional distribution given $x$. Example: mean estimation, etc..."}
\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies, but not sure?}
\raf{Isn't that what we do next anyway?  I think it's nice in 2.1}

@@

\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
\raft{Suggest ``target'' instead of original, based on Steinwart -- I think it's really clear that way}
One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
We want to lower-bound this dimension for a given learning problem.
\bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky. Then the bullet points explain the different settings.} \jessie{Adding a few sentences to try to address this... probably needs to be pared down.}
Consistency, which we formalize in Section~\ref{sec:consis-implies-indir}, is not very tractable.
Throughout the literature, consistency is defined in many subtlely different ways; some papers (e.g.\,\cite{ramaswamy2016convex,ramaswamy2018consistent}) refer to consistent \emph{algorithms} while others (e.g.\,\cite{bartlett2006convexity,tewari2007consistency}) refer to consistent \emph{losses}.
Even more confusing is the slight difference between considering consistency based on the sequence of functions learned from trianing on $m$ samples as opposed to learning over any general sequence of functions.
In general, consistency relies on both a surrogate and target loss, and until now, it has been unclear how to define consistency without a target loss. 
Ideally, we would have a more useful condition that could apply to all of the following settings:
\begin{itemize}
  \item The original prediction space is either \textbf{discrete}, e.g. a classification problem; or it is \textbf{continuous}, e.g. a regression or estimation problem.
  \item The original prediction problem is given either directly by a \textbf{loss} $\ell$, for which $L$ should be a surrogate; or it is given by a \textbf{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
\end{itemize}
We informally call the combinations of these characteristics the ``four quadrants'' of supervised learning problems.
For exmaple, one quadrant has problems that are continuous and specified by a property $\gamma$.
An example learning problem in this quadrant would be mean estimation: hypotheses should map $x$ to the mean of the conditional distribution $D_x$

@@

\raf{Same general comment on style, etc, as intro.  See if you can get the point across in fewer words.}\jessie{Took a pass on this as well.}
For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
%\raft{``Borda'', and anyway ML folks probably won't know what you mean}
However, optimizing over a target loss is often a computationally hard problem.
This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss, or property we want to predict, as is more common in the the continuous estimation setting.
A surrogate is no good on its own;we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.

@@

\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
In discrete prediction tasks, the two are in fact equivalent.  
\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification. 
\cite{ramaswamy2016convex} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
\cite{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, giving proofs for various classes of surrogate losses (i.e. margin-based, distance-based, supervised, unsupervised, etc.)
See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.

@@

We call a property $\gamma: \simplex \toto \R$ \emph{discrete} if $|\R| < \infty$, and we call a property \emph{set-valued} if there is a $p \in \simplex$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.
%Without much loss of generality, we assume that discrete properties are \emph{non-redundant}, meaning that for each $\gamma_r$, there is no $\gamma_{r'}$ such that $\gamma_{r'} \subseteq \gamma_r$.

Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \cite{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
Additionally, \cite{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider the discrete setting. \jessiet{right?}
%However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.

@@

While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and must be done deterministically.

>>>>

\section{Introduction}\label{sec:intro}
\raf{General comment: see if you can make the intro less of an explanation to someone who has never heard of consistency, etc, and more of a ``reminder'' and recap of what's been going on in the field, culminating in the gap between what is out there and what we would like to know -- the gap that we fill}
\raf{General style: see if you can make the writing sharper, with less passive voice.  See if you can channel some Hemmingway and boil each sentence down to the key point.}
\jessie{Alright, I tried...}
In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or there is no target loss.
When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
In continuous estimation settings, one typically starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value or an $\alpha$-quantile.
Here, we generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
%For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
\raft{I think few ML people know anything about pinball loss... I think we should de-emphasize the continuous setting in the intro, and include it in passing.}\jessiet{Removed the sentence, but probably want to at least allude to it?}
We desire a surrogate to be \emph{consistent}: a precursor to excess risk bounds and rates.
\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}\jessiet{Changed}
We are particularly interested in consistent \emph{and convex} surrogates% in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting. 
%We would also like our surrogate losses to be 
that are efficient in the dimension of the prediction, as this is one potential source of significant computational speedup.

%\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.  E.g. ``Our results give two contributions to this field.  First, .....  Second, .....''  Something like that before going into the theorems.}
Our results contribute two major findings.
First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
This lets us use property elicitation to bound the minimum prediction dimension needed to construct a consistent convex surrogate.
Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
\raft{Cleaned up this prev sentence} \jessiet{Noted... much better how it is now.}
The bounds we show in our second contribution (Theorem~\ref{thm:cvx-flats}) are general enough to apply across all four settings, and is the first bound to our knowledge to handle this generality.

@@

\raf{I'm usually against these sorts of sections if they are truly just a roadmap.  See if you can make it flow less like a table of contents and more like a list of contributions with references to where in the paper to find them.  E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.} \raft{Exactly, well done}\jessiet{Phew; feel free to delete this thread now.}
%actually tell the reader
After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
\raft{Not a characterization!}\jessiet{right.... whoops.}
the existence of consistent convex surrogates in a given dimension $d$.
This result is closely related to those provided by~\cite[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
Moreover, insights from our main result answer an open question posed by~\cite[Section 8]{frongillo2018elicitation} in the continuous estimation setting.

@@

We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.

In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to find a hypothesis $f$ that minimizes expected loss, $\E \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate prediction with $u \in \reals^d$.
A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and a surrogate $L$ is \emph{convex} if it is convex in the prediction space for every outcome $y \in \Y$.

@@

\bo{What about introducing the quadrants here? Something like: ``Instead of a target loss, in some estimation problems, one is given a target \emph{property}: [say what a property is]. The goal is to learn $f$ that approximately outputs the property on the conditional distribution given $x$. Example: mean estimation, etc..."}
\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies?}
\raf{Isn't that what we do next anyway?  I think it's nice in 2.1}

@@

\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{bartlett2006convexity}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
\raft{Suggest ``target'' instead of original, based on Steinwart -- I think it's really clear that way}
One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
We want to lower-bound this dimension for a given learning problem.
\bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky. Then the bullet points explain the different settings.} \jessie{Adding a few sentences to try to address this... probably needs to be pared down.}
Consistency, which we formalize in Section~\ref{sec:consis-implies-indir}, is not very tractable.
Throughout the literature, consistency is defined in many subtlely different ways; some papers (e.g.\,\cite{ramaswamy2016convex,ramaswamy2018consistent}) refer to consistent \emph{algorithms} while others (e.g.\,\cite{bartlett2006convexity,tewari2007consistency}) refer to consistent \emph{losses}.
Even more confusing is the slight difference between considering consistency based on the sequence of functions learned from training on $m$ samples as opposed to learning over any general sequence of functions. \jessiet{Can probably cut this sentence?}
In general, consistency relies on both a surrogate and target loss, and until now, it has been unclear how to define consistency without a target loss. 
Ideally, we would generalize consistency to apply to all of the following settings:
\begin{itemize}
  \item The original prediction space is either \textbf{discrete}, e.g. a classification problem; or it is \textbf{continuous}, e.g. a regression or estimation problem.
  \item The original prediction problem is given either directly by a \textbf{loss} $\ell$, for which $L$ should be a surrogate; or it is given by a \textbf{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
\end{itemize}
We informally call the combinations of these characteristics the ``four quadrants'' of supervised learning problems.
For exmaple, one quadrant has problems that are continuous and specified by a property $\gamma$.
An example learning problem in this quadrant would be mean estimation: hypotheses should map $x$ to the mean of the conditional distribution $D_x$

@@

\raf{Same general comment on style, etc, as intro.  See if you can get the point across in fewer words.}\jessie{Took a pass on this as well.}
For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
%\raft{``Borda'', and anyway ML folks probably won't know what you mean}
However, optimizing over a target loss is often a computationally hard problem.
This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss.%, or property we want to predict, as is more common in the the continuous estimation setting.
A surrogate is no good on its own; we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.

@@

\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
In discrete prediction tasks when given a target loss, the two are in fact equivalent.  
\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, it is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification. 
\cite{ramaswamy2016convex} further show necessary and sufficient conditions for discrete prediction problems to be consistent that can be applied to general discrete losses.
\cite{steinwart2007compare} generalizes the study of consistent losses from the discrete prediction setting and characterizes different types of loss functions, relating excess risk bounds, consistency, and calibration, studying various classes of surrogate losses (i.e. margin-based, distance-based, supervised, unsupervised, etc.)
See~\cite[Chapter 2]{steinwart2008support} for further discussion of these loss functions.
In Appendix~\ref{app:calibration}, we give a more general definition of calibration which is equivalent to Definition~\ref{def:calibrated-finite} in discrete prediction settings, but generalizes to continuous estimation settings.

@@

We call a property $\gamma: \simplex \toto \R$ \emph{discrete} if $|\R| < \infty$, and we call a property \emph{set-valued} if there is a $p \in \simplex$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
We use $\Gamma := \prop{L}$ to say $\Gamma$ is the (unique) property elicited by $L$.
%Without much loss of generality, we assume that discrete properties are \emph{non-redundant}, meaning that for each $\gamma_r$, there is no $\gamma_{r'}$ such that $\gamma_{r'} \subseteq \gamma_r$.

Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}, and \cite{finocchiaro2018convex} are among the first to consider \emph{convex} elicitable properties.
Additionally, \cite{agarwal2015consistent} are the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss, although they only consider settings with $|\Y| < \infty$. \jessiet{right?}
%However, their assumptions are more restrictive than ours; they only consider losses defined on the real line.% and assume the properties to be identifiable: an assumption we do not need.

@@

There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.
